### 2019-10-01 conflog.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this 
should be avoided. In this case we found that holding the conference at the end 
of April would conflict with finals for students and holding it earlier in 
March would conflict with several spring breaks as well as having potentially 
poorer weather. \textbf{A detailed graphical conflict schedule can be found in Appendix 
\ref{appendix:schedule} on page \pageref{appendix:schedule}.}

@@

The Illini Union is capable of hosting the entire technical program of the ANS 
Student Conference. This keeps the conference contained in one convenient 
location while being within easy access of the rest of the campus. Technical 
sessions will be held in a combination of rooms on the second, third, and 
fourth floors of The Union. Each of these rooms have at least enough capacity 
for 42 people, lecture style, and A/V capability. There will also be rooms 
available to have panels and workshops during the course of the technical 
program. The Illini Rooms A and B will be a combined space for the career fair 
while Illini Room C and the south lounge will host the poster sessions. We will 
keep the space open to allow the poster sessions and career fair to share 
attendance and encourage networking. A detailed list of room capacities and 
floor plans are located in Appendix \ref{appendix:building}: Building Layout on 
page \pageref{appendix:building}. \\

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
    \caption{The current 400-person banquet space at the IHotel is pictured 
        above. A new, 690-person ballroom will be available in 2020.}
\end{figure}

\subsubsection{Illini Union}
After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds. Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services. A floorplan for the Illini Rooms in rounds is available in Appendix D.\\

@@

\textbf{The I Hotel and Conference Center}\\
The IHotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\

@@

$\textbf{Illini Union}$\\
This is the primary hotel for invited speakers and panelists. Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held. The Union is also a five-minute walk from Green Street, the campus hub of dining and social activities. Guests have access to Wi-Fi and, upon request, guest passes to the university recreational facilities. Breakfast is provided in the form vouchers for any of the hotel restaurant options inside the Union. Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\

@@

$\textbf{Marriott TowneSuites}$\\
In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

@@

\begin{table}
\caption{Cost of Hotels}
\label{table:hotels}
	\centering
	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
	\hline\hline
	\textbf{Hotel} & \textbf{Distance from} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
                & \textbf{the Union (mi)} & & & & \\
	\hline\hline
	Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
	Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
	Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
	\hline
	\end{tabular}}
\subcaption*{\textbf{*}\textit{Price for a queen double}\\ \textbf{**}\textit{Assumes 4 people per room}}
\end{table}

@@

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

>>>>

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A on page \pageref{appendix:schedule}.

@@

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout on page \pageref{appendix:building}. \\

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
    \caption{The current 400-person banquet space at the IHotel.}
\end{figure}

\subsubsection{Illini Union}
The final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds. Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services. A floorplan for the Illini Rooms in rounds is available in Appendix D.\\

@@

\textbf{The I Hotel and Conference Center}\\
The I Hotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\

@@

$\textbf{Illini Union}$\\
This is the primary hotel for invited speakers and panelists. Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held. The Union is also a five-minute walk from Green Street, the campus hub of dining and social activities. Guests have access to Wi-Fi and, upon request, guest passes to the university recreational facilities. Breakfast is provided in the form of vouchers for any of the hotel restaurant options inside the Union. Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\

@@

$\textbf{Marriott TownePlace Suites}$\\
In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TownePlace Suites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

@@

\begin{table}
\caption{Cost of Hotels}
\label{table:hotels}
	\centering
	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
	\hline\hline
	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
	\hline\hline
	Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
	Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
	Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
	\hline
	\end{tabular}}
\subcaption*{\textbf{*}\textit{Price for a queen double} \textbf{**}\textit{Assumes 4 people per room}}
\end{table}

@@

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. Due to the central location of Champaign-Urbana, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

### 2019-10-01 socials.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

>>>>

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Illini Union! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

### 2019-10-01 theme.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

\section{Saving the World One Atom at a Time}
The future is nuclear. There are many grand challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems. Nuclear, plasma, and radiological engineering will be central to many endeavors, whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer. By hosting this conference, we hope to inspire and motivate students in these engineering fields to tackle big problems. Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress. This conference is about science and engineering and it is about the people that make science and engineering possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
There are three main goals of our theme and each of these goals will be the focus of a different day of the student conference.
\begin{enumerate}
	\item Celebrate the people behind the science and engineering.\\
	Everyone that does science has a unique background, skillset, and experiences. People are what make science possible. Encouraging diversity and inclusivity in these areas, and others, improve creativity, productivity, and insights. We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
	\item Connect students and professionals to develop strong networks.\\
	This is the networking and professional-development-focused section of the conference. Beyond the mere job-seeking aspect, these networks enable the spread of ideas. Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people. More diverse networks are better networks. This aspect of the conference is captured by workshops like \textit{Developing Your Network}. 
	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
	The final day is the culmination of the conference and underpins the single unifying ideal. For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers. Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to improve the world around them.  
\end{enumerate}
These goals and our theme motivated every decision in our conference proposal. The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\

>>>>

\section{Saving the World One Atom at a Time}
The future is nuclear. There are many grand challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems. Nuclear, plasma, and radiological engineering will be central to many endeavors, whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer. By hosting this conference, we hope to inspire and motivate students in these engineering fields to tackle big problems. Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress. This conference is about science and engineering and it is about the people that make science and engineering possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
There are three main goals of our theme and each of these goals will be the focus of a different day of the student conference.
\begin{enumerate}
	\item Celebrate the people behind the science and engineering.\\
	Everyone that does science has a unique background, skillset, and experiences. People are what make science possible. Encouraging diversity and inclusivity in these areas, and others, improve creativity, productivity, and insights. We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
	\item Connect students and professionals to develop strong networks.\\
	This is the networking and professional-development-focused section of the conference. Beyond the mere job-seeking aspect, these networks enable the spread of ideas. Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people. More diverse networks are better networks. This aspect of the conference is captured by workshops like \textit{Developing Your Network}. 
	\item Inspire the next generation of nuclear engineers to take on grand challenge problems.\\
	The final day is the culmination of the conference and underpins the single unifying ideal. For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers. Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to improve the world around them.  
\end{enumerate}
These goals and our theme motivated every decision in our conference proposal. The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\
